A pipeline to analyse time-course gene expression data

### 2019-08-12 scripts/manuscript.Rmd
FIX to the code

```{r echo=FALSE}
kable(contrasts,col.names="Contrasts")
```
**EAP: Not sure if `kable` is better than just printout?**

@@

```{r weekly_differential_analysis}
# Define contrast	
VL_weekly_de_analysis = DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)
```
**EAP: Sort of strange to have argument `spines_model` for function that doesn't use splines. Perhaps there is a generic name that could be used for the argument**

@@

```{r fig.width=6, fig.height=6, echo=FALSE}
timely_barplot = function(de_analysis, labels=NULL, qval_threshold=0.05, title="",...){
    qval_colnames = colnames(de_analysis)[
	grepl("qval", colnames(de_analysis))]
    if(is.null(labels)) labels<-sapply(strsplit(gsub("-qval","",qval_colnames),"\\."),.subset2,3)
    number_de_genes_per_time = colSums(de_analysis[, qval_colnames] < 0.05)
    barplot(number_de_genes_per_time, col="black", 
            names.arg=labels,ylim=c(0, 20000),
	    xlab="Timepoint", ylab="Number of DE genes", main=title,...)

}

par(mfrow=c(2, 2))
timely_barplot(K_weekly_de_analysis, time, title="Kawasaki",las=3)
timely_barplot(C_weekly_de_analysis, time, title="California",las=3)
timely_barplot(VL_weekly_de_analysis, time, title="Vietnam low-dose",las=3)
timely_barplot(VH_weekly_de_analysis, time, title="Vietnam high-dose",las=3)
```

>>>>

```{r echo=FALSE}
kable(contrasts, col.names="Contrasts")
```
**EAP: Not sure if `kable` is better than just printout?**

@@

```{r weekly_differential_analysis}
# Define contrast	
weekly_de_analysis = DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)
```
**EAP: Sort of strange to have argument `spines_model` for function that doesn't use splines. Perhaps there is a generic name that could be used for the argument**

@@

```{r fig.width=6, fig.height=6, echo=FALSE}
timely_barplot = function(de_analysis, labels=NULL, qval_threshold=0.05,
			  title="", ...){
    qval_colnames = colnames(de_analysis)[
	grepl("qval", colnames(de_analysis))]
    if(is.null(labels)){
	labels = sapply(
	    strsplit(gsub("-qval", "", qval_colnames), "\\."), .subset2, 3)
    }
    number_de_genes_per_time = colSums(de_analysis[, qval_colnames] < 0.05)

    barplot(number_de_genes_per_time, col="black", 
            # names.arg=labels,
	    ylim=c(0, 20000),
	    xlab="Timepoint", ylab="Number of DE genes", main=title, ...)  
}

par(mfrow=c(2, 2))
timely_barplot(K_weekly_de_analysis, time, title="Kawasaki", las=3)
timely_barplot(C_weekly_de_analysis, time, title="California", las=3)
timely_barplot(VL_weekly_de_analysis, time, title="Vietnam low-dose", las=3)
timely_barplot(VH_weekly_de_analysis, time, title="Vietnam high-dose", las=3)
```
